Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/barriers.tex
small edits about barriers

\begin{finding}
\textit{When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation. However, when the incumbent plays $\DEG$ or $DG$ there is no substantial difference between the two.}
\end{finding}

>>>>

\begin{finding}
\textit{Both the data advantage and reputation advantage alone serve as strong barriers to entry. When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation, but when the incumbent plays $\DEG$ or $DG$ there is no substantial difference between the two.}
\end{finding}

### 2018-08-30 paper/content/introduction.tex
small edits about barriers

Our findings on temporary monopoly shed light on the ``first-mover advantage" phenomenon in the digital economy. In this scenario, the incumbent firm enjoys both a ``data advantage" and a ``reputational advantange". We further investigate which of the two is a stronger barrier to entry. \ascomment{and find what? and what's the new intuition?}

>>>>

Our findings on temporary monopoly shed light on the ``first-mover advantage" phenomenon in the digital economy. In this scenario, the incumbent firm enjoys both a ``data advantage" and a ``reputational advantage". We further investigate which of the two is a stronger barrier to entry. \ascomment{and find what? and what's the new intuition?} \gaedit{We find that retaining either the reputation or the data advantage alone still serves as a strong barrier to entry, but that the data barrier to entry is only consistently stronger when the incumbent commits to a more advanced exploration algorithm. }
